[Artifact Presentation] Damegender: \\ Writing and Comparing Gender Detection Tools

### 2020-07-19 paper2sattose.tex
paper2sattose.tex: replace Namsor by Namsor (v1)

\begin{abstract}
%Context
Diversity in software development teams has been identified as one of the main ingredients of a more productive, more healthy software community.
Thus, the interest of the research community in identifying who is contributing to a project has increased in the last years.
In the software domain, and although other types of diversity exist, this is particularly important for the case of gender.
% Objective, 
Given the large amount of publicly available data on the software development process that can be retrieved and analyzed from the Internet (e.g., GitHub, StackOverflow), the importance of having methods and tools that help to identify the participation of women within large amounts of data is desirable.
% Method name-to-gender inference
In this paper we present a free software tool, called \texttt{damegender}, which we have conceived to infer the gender from the name of a participant.
\texttt{damegender} is based on open databases from official census and uses Machine Learning.
An experimental branch is currently under development for those cases where instead of names we have diminutives or nicknames.
% Results 
We have compared \texttt{damegender} with other name-to-gender inference tools, obtaining good results.
% Conclusions.
We hope the \texttt{damegender} tool can become a cornerstone for the scientific advancement of the study of gender (including the gender gap) and diversity in the IT, and in particular in the free software community.
\end{abstract}

@@

The interest on gender diversity has become more and more relevant, and so does the identification methods that allow to perform comprehensive studies on gender representation, given the large amounts of data available, in particular from collaborative environments.

The most used method to infer the gender of participants is by looking at their name.
However, there are some studies about Twitter or GitHub were not only names to detect gender. 
In them we can find gender detection tools that infer the gender from faces in images~\cite{ranjan2017hyperface}, from hand-written annotations~\cite{liwicki2011automatic}, or from speeches~\cite{koppel2002automatically}.

Currently, there are different ways to detect gender from a person's name (and maybe other personal data, such as the surname, the geographic location, etc.).
A first one is based on data extracted from the Wikipedia, self-references in trust websites, searches in Google Images, among others.
Another way to do it is by using one of the existing Application Programming Interfaces (APIs).
This paper is about the latter, focusing on their possibilities and limitations.
Therefore, (i) we evaluate the quality (and accessibility, including price) of different existing solutions;
(ii) we discuss about their limitations; and
(iii) we investigate what happens with those names not included in a census, for example, nicknames or diminutives.
% and (iv) we elaborate on how massive gender detection from Internet, for example, mailing lists or software repositories, can be done.

@@

(ii) a tool, called \texttt{damegender}, guessing gender from a name
  giving support to Spanish and English from the open data census
  provides by the states built to understand current technologies in
  detail; this tools has been compared with APIs using an international
  dataset with good results; and

(iii) a machine learning solution to strings not found in the census
  dataset to approach the problem with nicknames and diminutives; and

@@

In \texttt{damegender}, we are including Open Data census about names and gender, usually offered by governments, such as the ones from Spain (by means of INE.es, the Spanish National Statistics Institute), Uruguay, USA and United Kingdom. 
%The datasets provided by the software package is incrementing the speed retrieving data.

@@

Some Open Datasets, such the one offered by INE.es or the government of the United States of America offer support for surnames and how they are related to ethnicity. 
In particular, the dataset from the government of the United States of America offers a probability of the race, and the Spanish INE.es gives the number of people with a surname with a nationality different to the Spanish nationality.

@@

Standard commercial name-to-gender inference Application Programming Interfaces (APIs) usually guess the gender for a single name or a list of names (from a CSV file or an API call). 
To express geolocalization the user can also give surnames, a country ISO code, or specify a language.
Generally, you can give a probability and a counter associated to a name and gender in a certain population.

@@

We have used this comparison framework and have updated it to the current situation and extended it with \texttt{damegender}.
Results can be found in Table~\ref{table:comparison}.
As it can be observed, commercial services have the advantage of owning large datasets, in the order of millions or even of billions of entries.
The most advanced ones offer support for non-Latin alphabets.
On the other side, they limit the amount of free requests that can be performed and their costs range from 7 euro to 150 euro per month.

@@

%\begin{table*}[]{@{}lllllll@{}}
\begin{table}[t]
\footnotesize
\begin{tabular}[]{lcccc}
  \hline
  API & Acc & Prec & F1 & Recall\tabularnewline
\hline
Genderapi & 0.969 & 0.972 & 0.964 & 1.0\tabularnewline
Genderize & 0.927 & 0.976 & 0.966 & 1.0\tabularnewline
Damegender (SVC)\footnote{SVC is the acronym of Support Vector Classification, the Machine Learning algorithm that Damegender was using with this results} & 0.879 & 0.972 & 0.972 & 1.0\tabularnewline
Namsor & 0.867 & 0.973 & 0.924 & 1.0\tabularnewline
Nameapi & 0.830 & 0.974 & 0.905 & 1.0\tabularnewline
Gender Guesser & 0.774 & 0.985 & 0.872 & 1.0\tabularnewline
\hline
\end{tabular}
\caption{Comparison of measures of the quality of the results for the tools under study.}
\label{table:DifferentAccuraciesMeasures}
\end{table}

In this section, we will analyze the quality of service of existing name-to-gender inference services and tools.
There are different ways to express the probability of a successful identification (e.g., confidence, scale, accuracy, precision, recall).
We can also inspect the confusion matrix to understand where the tools and services succeed or fail, and to analyze the different errors measures (error coded, error coded without not applicable values, error gender bias, not applicable coded) that appear.

Santamaría and Mihaljevi\'c~\cite{10.7717/peerj-cs.156} explain different ways to determine gender from a name; they offer 7,000 names that can serve as the \emph{golden set} to evaluate them. 
In their dataset, gender is classified as male, female or unknown. 
We have used this dataset, not considering the unknown variable, for our experiments.

The results, using common information retrieval metrics, can be seen in Table~\ref{table:DifferentAccuraciesMeasures}.
Accuracy is the ratio of correctly predicted observation to the total observations.
It should be noted that \emph{Accuracy} can be a misleading metric for imbalanced data sets, such as the ones that we usually have in software development projects~\cite{ghosh2002free}.
This is because for a sample with 85 negative and 15 positive values, classifying all values as negative would give an accuracy score of 0.85.
In those cases, it is better to report other measures, such as the balanced accuracy, which normalizes true positive and true negative predictions by the number of positive and negative samples~\cite{mower2005prep}.
As Santamaría and Mihaljevi\'c's data does not come from the IT domain, we can use accuracy in our research.
Precision is the fraction of relevant instances among the retrieved instances.
Recall is the fraction of the total amount of relevant instances that were actually retrieved.
In our case, we have left no name out, so recall is 1 for all tools.
Precision and recall are sometimes used together in the F1 Score (or f-measure) to provide a single measurement for a system.
As can be observed, \texttt{Genderapi} and \texttt{Genderize} obtain the best results -- although all solutions are close and reach results better than 0.8 for accuracy, except for \texttt{Gender Guesser}.
\texttt{damegender} offers relatively good results.
Given, on the other hand, that its focus is mainly to be used in the IT domain, where the gender is highly imbalanced, we are very positive about its precision, as accuracy is not that relevant as noted above.

@@

\begin{table}[t]
\footnotesize
\begin{tabular}[]{lrrrr}
  \hline
  APIs          & gender & male & female & undef \tabularnewline
\hline
%%\endhead
Genderapi         & male    & 3589 & 155  &  67 \tabularnewline
                  & female  & 211  & 1734 &  23 \tabularnewline
Damegender       & male    & 3663 & 147  &   0 \tabularnewline
(SVC)\footnotemark[1] & female  & 551  & 1497 &   0 \tabularnewline
Genderguesser     & male    & 3326 &  139 & 346 \tabularnewline
                  & female  & 78   & 1686 & 204 \tabularnewline
Namsor            & male    & 3325 & 139  & 346 \tabularnewline
                  & female  & 78   & 1686 & 204 \tabularnewline
Genderize         & male    & 3157 & 242  & 412 \tabularnewline
                  & female  & 75   & 1742 & 151 \tabularnewline
Nameapi           & male    & 2627 & 674  & 507 \tabularnewline
                  & female  & 667  & 1061 & 240 \tabularnewline 
\hline
\end{tabular}
\caption{Confusion matrix tables by APIs}
\label{table:ConfusionMatrixTables}
\end{table}

We have performed a comparison using a confusion matrix for the software/tools under study (see Table~\ref{table:ConfusionMatrixTables}).
These results are very similar to the ones reported in~\cite{10.7717/peerj-cs.156}, which offers confidence that we have done our comparison correctly.
The most important tools (\texttt{Namsor}, \texttt{Genderapi} and \texttt{Genderize}) improve the values of accuracy with respect to the previous comparison.
In particular, \texttt{Genderapi} improves the results for \emph{undefined}.
For \texttt{Genderize}, we obtain exactly the same results. 
For \texttt{Genderguesser}, however, we obtain different results, which is to some extent not expected, because the software has not been modified for several years.
\texttt{Nameapi}'s results is changing from male to female with more errors. 
In \texttt{Namsor}, the results are similar. 
\texttt{damegender} is not guessing undefined because we predict with machine learning (using an SVC algorithm) if the string is not in the database.

\begin{table*}
\footnotesize
\center
\begin{tabular}[]{lrrrr}
\hline
API & error & error w/o na & na coded & error gender bias\tabularnewline
\hline
%\endhead
Damegender (SVC)\footnotemark[1] & 0.121 & 0.121 & 0.0 & -0.07\tabularnewline
GenderApi & 0.167 & 0.167 & 0.0 & -0.167\tabularnewline
Gender Guesser & 0.225 & 0.027 & 0.204 & 0.003\tabularnewline
Genderize & 0.276 & 0.261 & 0.0204 & -0.0084 \tabularnewline 
Namsor & 0.332 & 0.262 & 0.095 & 0.01 \tabularnewline
Nameapi & 0.361 & 0.267 & 0.129 & 0.001 \tabularnewline
\hline
\end{tabular}
\caption{APIs and Errors}
\vspace{0.3cm}
\label{table:ApisAndErrors}
\end{table*}

In Table~\ref{table:ApisAndErrors} we can see the different measures for errors in the APIs.
\emph{Error coded} defines if the true is different than the guessed one. 
\emph{Error coded without na} defines if the true is different than the guessed one, but without undefined results.
\emph{Error gender bias} allows to understand if the error is bigger for guessing males than females or viceversa.
The \emph{weighted error} defines if the true value is different than the guessed one, but giving a weight to the guessed as undefined.
The most relevant information is a high index of errors for \texttt{Nameapi} and \texttt{Namsor},
while \texttt{GenderApi} and \texttt{damegender} have a low index of errors.

@@

\begin{table*}
\footnotesize
\center
\begin{tabular}[]{lccccccc}
  \hline
Dataset & contains a & last is a & last is o & last is consonant & last is vocal & 1st is consonant & 1st is vocal  \tabularnewline
  \hline
  %\endhead
 Uruguay (F) &    0.816 &         0.456 &         0.007 &                 0.287 &             0.712 &                  0.823 &              0.177  \tabularnewline
 Uruguay (M) &    0.643 &         0.249 &         0.062 &                 0.766 &             0.234 &                  0.771 &              0.228  \tabularnewline
 Spain (F)   &    0.922 &         0.588 &          0.030 &                 0.271 &             0.728 &                  0.772 &              0.228  \tabularnewline
 Spain (M)   &    0.818 &          0.030 &         0.268 &                 0.569 &              0.430 &                  0.763 &              0.236  \tabularnewline
 UK (F)      &    0.825 &         0.374 &         0.013 &                 0.322 &             0.674 &                  0.765 &              0.235  \tabularnewline
 UK (M)      &    0.716 &         0.036 &         0.039 &                  0.780 &             0.218 &                  0.799 &                0.200  \tabularnewline
 USA (F)     &    0.816 &         0.456 &         0.007 &                 0.287 &             0.712 &                  0.823 &              0.177  \tabularnewline
 USA (M)     &    0.643 &          0.020 &         0.061 &                 0.765 &             0.234 &                   0.840 &              0.159  \tabularnewline
 Canada (F)  &    0.659 &         0.189 &         0.005 &                 0.591 &             0.408 &                  0.838 &              0.160  \tabularnewline
 Canada (M)  &    0.752 &          0.220 &         0.025 &                  0.540 &             0.456 &                  0.818 &              0.181  \tabularnewline
Australia (F)      &    0.922 &         0.588 &         0.033 &                 0.272 &             0.728 &                  0.772 &              0.228 \tabularnewline
 Australia (M)        &    0.818 &          0.030 &         0.269 &                  0.570 &              0.430 &                  0.763 &              0.237 \tabularnewline

@@

We have developed some additional experimental functionality that allows to analyze our database according to some features using machine learning algorithms.
To test our approach, we have selected some features of names, such as a being the first letter, a (or o) being the last letter, contains the letter a, first letter is a vocal, last letter is a vocal, last letter is a consonant, or last letter is a. 
The selection of the features was verified with Principal Component Analysis.
The datasets used in this experiment were the ones from the National Institute of Statistics (Spain, Uruguay, United Kingdom, United States of America, Australia and Canada).
The most relevant results for the different datasets used are offered in Table~\ref{table:InfoFeatures}.

@@

For instance, the feature \emph{containing the letter a in the name} varies 0.2 from males to females for USA and Uruguay, and 0.1 from males to females for United Kingdom, Australia and Spain.
The feature \emph{the last letter is an a} varies 0.5 from males to females for Australia and Spain, around 0.4 for USA and United Kingdom and 0.2 in
Uruguay.
The feature \emph{the last letter is an o} varies 0.2 in (Spain, Australia) from females to males and is equal in Uruguay, USA, United Kingdom.
For the feature \emph{the last letter is a consonant} all countries give as a result that males do have it more frequently, with results that range from 0.3 to 0.5: Uruguay and USA (0.5), United Kingdom (0.4), Australia and Spain (0.3). 
So, the feature \emph{the last letter is a vocal} is, as expected, the reverse of the feature \emph{the last letter is a consonant}. 
The features \emph{the first letter is a consonant} or \emph{the first letter is a vocal} are, however, non-significant as they offer similar results in English and Spanish.

>>>>

\begin{abstract}
%Context
Diversity in software development teams has been identified as one of the main ingredients of a more productive and healthy software community.
Thus, the interest of the research community in identifying who is contributing to a project has increased in the last years.
In the software domain, and although other types of diversity exist, this is particularly important for the case of gender.
% Objective, 
Given the large amount of publicly available data on the software development process that can be retrieved and analyzed from the Internet (e.g., GitHub, StackOverflow), the importance of having methods and tools that help to identify the participation of women within large amounts of data is desirable.
% Method name-to-gender inference
In this paper we present a free software tool, called \texttt{damegender}, which we have conceived to infer the gender from the name of a participant.
\texttt{damegender} is based on open databases from official census and uses Machine Learning.
An experimental branch is currently under development for those cases where instead of names we have diminutives or nicknames.
% Results 
We have compared \texttt{damegender} with other name-to-gender inference tools, obtaining good results.
% Conclusions.
We hope the \texttt{damegender} tool can become a cornerstone for the scientific advancement of the study of gender (including the gender gap) and diversity in Information Technology (IT), and in particular in the free software community.
\end{abstract}

@@

The interest on gender diversity has become more and more relevant, and so does the identification methods that allow us to perform comprehensive studies on gender representation, given the large amounts of data available, in particular from collaborative environments.

The most used method to infer the gender of participants is by looking at their name.
However, there are some studies about Twitter and GitHub where not only names are used to detect gender. 
In those studies we can find gender detection tools that infer the gender from faces in images~\cite{ranjan2017hyperface}, from hand-written annotations~\cite{liwicki2011automatic}, or from speeches~\cite{koppel2002automatically}.

Currently, there are different ways to detect gender from a person's name (and maybe other personal data, such as the surname, the geographic location, etc.).
A first one is based on data extracted from the Wikipedia, self-references in trust websites, searches in Google Images, among others.
Another way to do it is by using one of the existing Application Programming Interfaces (APIs).
This paper is about the latter, focusing on their possibilities and limitations.
Therefore, (i) we evaluate the quality (and accessibility, including price) of different existing solutions;
(ii) we discuss their limitations; and
(iii) we investigate what happens with those names not included in a census, for example, nicknames or diminutives.
% and (iv) we elaborate on how massive gender detection from Internet, for example, mailing lists or software repositories, can be done.

@@

(ii) a tool, called \texttt{damegender}, guessing gender from a name
  giving support to Spanish and English from the open data census
  provides by the states built to understand current technologies in
  detail; this tool has been compared with APIs using an international
  dataset with good results; and

(iii) a machine learning solution to strings not found in the census
  dataset to approach the problem with nicknames and diminutives;

@@

In \texttt{damegender}, we are including Open Data census about names and gender, usually offered by governments, such as the ones from Spain (by means of INE.es, the Spanish National Statistics Institute), Uruguay, USA and UK. 
%The datasets provided by the software package is incrementing the speed retrieving data.

@@

Some Open Datasets, such the one offered by INE.es or the government of the US offer support for surnames and how they are related to ethnicity. 
In particular, the dataset from the government of the US offers a probability of the race, and the Spanish INE.es gives the number of people with a surname with a nationality different to the Spanish nationality.

@@

Standard commercial name-to-gender inference APIs usually guess the gender for a single name or a list of names (from a CSV file or an API call). 
To express geolocalization the user can also give surnames, a country ISO code, or specify a language.
Generally, you can give a probability and a counter associated to a name and gender in a certain population.

@@

We have used this comparison framework and have updated it to the current situation and extended it with \texttt{damegender}.
Results can be found in Table~\ref{table:comparison}.
As it can be observed, commercial services have the advantage of owning large datasets, in the order of millions or even of billions of entries.
The most advanced ones offer support for non-Latin alphabets.
However, they limit the amount of free requests that can be performed and their costs range from 7 euro to 150 euro per month.

@@

%\begin{table*}[]{@{}lllllll@{}}
\begin{table}[t]
\footnotesize
\begin{tabular}[]{lcccc}
  \hline
  API & Acc & Prec & F1 & Recall\tabularnewline
\hline
Genderapi & 0.969 & 0.972 & 0.964 & 1.0\tabularnewline
Genderize & 0.927 & 0.976 & 0.966 & 1.0\tabularnewline
Damegender (SVC)\footnote{SVC is the acronym of Support Vector Classification, the Machine Learning algorithm that Damegender was using with this results} & 0.879 & 0.972 & 0.972 & 1.0\tabularnewline
Namsor (v1) & 0.867 & 0.973 & 0.924 & 1.0\tabularnewline
Nameapi & 0.830 & 0.974 & 0.905 & 1.0\tabularnewline
Gender Guesser & 0.774 & 0.985 & 0.872 & 1.0\tabularnewline
\hline
\end{tabular}
\caption{Comparison of measures of the quality of the results for the tools under study.}
\label{table:DifferentAccuraciesMeasures}
\end{table}

In this section, we will analyze the quality of the service of existing name-to-gender inference services and tools.
There are different ways to express the probability of a successful identification (e.g., confidence, scale, accuracy, precision, and recall).
We can also inspect the confusion matrix to understand where the tools and services succeed or fail, and to analyze the different errors measures (error coded, error coded without not applicable values, error gender bias, not applicable coded) that can happen.

Santamaría and Mihaljevi\'c~\cite{10.7717/peerj-cs.156} explain different ways to determine gender from a name; they offer 7,000 names that can serve as the \emph{golden set} to evaluate them. 
In their dataset, gender is classified as male, female, or unknown. 
We have used this dataset, not considering the unknown variable, for our experiments.

The results, using common information retrieval metrics, can be seen in Table~\ref{table:DifferentAccuraciesMeasures}.
Accuracy is the ratio of correctly predicted observation to the total observations.
It should be noted that \emph{Accuracy} can be a misleading metric for imbalanced data sets, such as the ones that we usually have in software development projects~\cite{ghosh2002free}.
This is because for a sample with 85 negative and 15 positive values, classifying all values as negative would give an accuracy score of 0.85.
In those cases, it is better to report other measures, such as the balanced accuracy, which normalizes true positive and true negative predictions by the number of positive and negative samples~\cite{mower2005prep}.
As Santamaría and Mihaljevi\'c's data does not come from the IT domain, we can use accuracy in our research.
Precision is the fraction of relevant instances among the retrieved instances.
Recall is the fraction of the total amount of relevant instances that were actually retrieved.
In our case, we have left no name out, so recall is 1 for all tools.
Precision and recall are sometimes used together in the F1 Score (or f-measure) to provide a single measurement for a system.
As can be observed, \texttt{Genderapi} and \texttt{Genderize} obtain the best results -- although all solutions are close and reach results better than 0.8 for accuracy, except for \texttt{Gender Guesser}.
\texttt{damegender} offers relatively good results.
Given, however, that its focus is mainly to be used in the IT domain, where the gender is highly imbalanced, we are very positive about its precision, as accuracy is not that relevant as noted above.

@@

\begin{table}[t]
\footnotesize
\begin{tabular}[]{lrrrr}
  \hline
  APIs          & gender & male & female & undef \tabularnewline
\hline
%%\endhead
Genderapi         & male    & 3589 & 155  &  67 \tabularnewline
                  & female  & 211  & 1734 &  23 \tabularnewline
Damegender        & male    & 3663 & 147  &   0 \tabularnewline
                  & female  & 551  & 1497 &   0 \tabularnewline
Genderguesser     & male    & 3326 &  139 & 346 \tabularnewline
                  & female  & 78   & 1686 & 204 \tabularnewline
Namsor (v1)       & male    & 3325 & 139  & 346 \tabularnewline
                  & female  & 78   & 1686 & 204 \tabularnewline
Genderize         & male    & 3157 & 242  & 412 \tabularnewline
                  & female  & 75   & 1742 & 151 \tabularnewline
Nameapi           & male    & 2627 & 674  & 507 \tabularnewline
                  & female  & 667  & 1061 & 240 \tabularnewline 
\hline
\end{tabular}
\caption{Confusion matrix tables by APIs}
\label{table:ConfusionMatrixTables}
\end{table}

We have performed a comparison using a confusion matrix for the software/tools under study (see Table~\ref{table:ConfusionMatrixTables}).
These results are very similar to the ones reported in~\cite{10.7717/peerj-cs.156}, which offers confidence that we have done our comparison correctly.
The most important tools (\texttt{Namsor (v1)}, \texttt{Genderapi}, and \texttt{Genderize}) improve the values of accuracy with respect to the previous comparison.
In particular, \texttt{Genderapi} improves the results for \emph{undefined}.
For \texttt{Genderize}, we obtain exactly the same results. 
For \texttt{Genderguesser}, however, we obtain different results, which is to some extent not expected, because the software has not been modified for several years.
\texttt{Nameapi}'s results is changing from male to female with more errors. 
In \texttt{Namsor (v1)}, the results are similar. 
\texttt{damegender} is not guessing undefined because we predict with machine learning (using an SVC algorithm) if the string is not in the database.

\begin{table*}
\footnotesize
\center
\begin{tabular}[]{lrrrr}
\hline
API & error & error w/o na & na coded & error gender bias\tabularnewline
\hline
%\endhead
Damegender (SVC)\footnotemark[1] & 0.121 & 0.121 & 0.0 & -0.07\tabularnewline
GenderApi & 0.167 & 0.167 & 0.0 & -0.167\tabularnewline
Gender Guesser & 0.225 & 0.027 & 0.204 & 0.003\tabularnewline
Genderize & 0.276 & 0.261 & 0.0204 & -0.0084 \tabularnewline 
Namsor (v1) & 0.332 & 0.262 & 0.095 & 0.01 \tabularnewline
Nameapi & 0.361 & 0.267 & 0.129 & 0.001 \tabularnewline
\hline
\end{tabular}
\caption{APIs and Errors}
\vspace{0.3cm}
\label{table:ApisAndErrors}
\end{table*}

In Table~\ref{table:ApisAndErrors} we can see the different measures
for errors in the APIs.  \emph{Error coded} defines if the true is
different than the guessed one.  \emph{Error coded without na} defines
if the true is different than the guessed one, but without undefined
results.  \emph{Error gender bias} allows to understand if the error
is bigger for guessing males than females or viceversa.  The
\emph{weighted error} defines if the true value is different than the
guessed one, but giving a weight to the guessed as undefined.  The
most relevant information is a high index of errors for
\texttt{Nameapi} and \texttt{Namsor (v1)}, while \texttt{GenderApi}
and \texttt{damegender} have a low index of errors.

@@

\begin{table*}
\footnotesize
\center
\begin{tabular}[]{lccccccc}
  \hline
Dataset & contains a & last is a & last is o & last is consonant & last is vowel & 1st is consonant & 1st is vowel  \tabularnewline
  \hline
  %\endhead
 Uruguay (F) &    0.816 &         0.456 &         0.007 &                 0.287 &             0.712 &                  0.823 &              0.177  \tabularnewline
 Uruguay (M) &    0.643 &         0.249 &         0.062 &                 0.766 &             0.234 &                  0.771 &              0.228  \tabularnewline
 Spain (F)   &    0.922 &         0.588 &          0.030 &                 0.271 &             0.728 &                  0.772 &              0.228  \tabularnewline
 Spain (M)   &    0.818 &          0.030 &         0.268 &                 0.569 &              0.430 &                  0.763 &              0.236  \tabularnewline
 UK (F)      &    0.825 &         0.374 &         0.013 &                 0.322 &             0.674 &                  0.765 &              0.235  \tabularnewline
 UK (M)      &    0.716 &         0.036 &         0.039 &                  0.780 &             0.218 &                  0.799 &                0.200  \tabularnewline
 USA (F)     &    0.816 &         0.456 &         0.007 &                 0.287 &             0.712 &                  0.823 &              0.177  \tabularnewline
 USA (M)     &    0.643 &          0.020 &         0.061 &                 0.765 &             0.234 &                   0.840 &              0.159  \tabularnewline
 Canada (F)  &    0.659 &         0.189 &         0.005 &                 0.591 &             0.408 &                  0.838 &              0.160  \tabularnewline
 Canada (M)  &    0.752 &          0.220 &         0.025 &                  0.540 &             0.456 &                  0.818 &              0.181  \tabularnewline
Australia (F)      &    0.922 &         0.588 &         0.033 &                 0.272 &             0.728 &                  0.772 &              0.228 \tabularnewline
 Australia (M)        &    0.818 &          0.030 &         0.269 &                  0.570 &              0.430 &                  0.763 &              0.237 \tabularnewline

@@

We have developed some additional experimental functionality that allows to analyze our database according to some features using machine learning algorithms.
To test our approach, we have selected some features of names, such as a being the first letter, a (or o) being the last letter, contains the letter a, first letter is a vowel, last letter is a vowel, last letter is a consonant, or last letter is a. 
The selection of the features was verified with Principal Component Analysis.
The datasets used in this experiment were the ones from the National Institute of Statistics (Spain, Uruguay, United Kingdom, United States of America, Australia and Canada).
The most relevant results for the different datasets used are offered in Table~\ref{table:InfoFeatures}.

@@

For instance, the feature \emph{containing the letter a in the name} varies 0.2 from males to females for USA and Uruguay, and 0.1 from males to females for United Kingdom, Australia, and Spain.
The feature \emph{the last letter is an a} varies 0.5 from males to females for Australia and Spain, around 0.4 for USA and United Kingdom and 0.2 in
Uruguay.
The feature \emph{the last letter is an o} varies 0.2 in (Spain, Australia) from females to males and is equal in Uruguay, USA, United Kingdom.
For the feature \emph{the last letter is a consonant} all countries give as a result that males do have it more frequently, with results that range from 0.3 to 0.5: Uruguay and USA (0.5), United Kingdom (0.4), Australia and Spain (0.3). 
So, the feature \emph{the last letter is a vowel} is, as expected, the reverse of the feature \emph{the last letter is a consonant}. 
The features \emph{the first letter is a consonant} or \emph{the first letter is a vowel} are, however, non-significant as they offer similar results in English and Spanish.
